---
title: "Master RMD"
author: "James C"
date: "4/30/2020"
output: pdf_document
---


#241 Final Project

##Clean Up Data
```{r}
library(haven)
library(dplyr)
togo_data_dhs <- read_dta("togo data dhs.dta")
new_data <- togo_data_dhs
new_data <- as.data.frame(new_data)
new_data <- new_data %>% select("v012", 
"v302a", 
"mv034b_1", 
"v190", 
"mv106",
"mv151",
"mv035", 
"v130",
"v312", 
"v362", 
"v393", 
"v394")

colnames(new_data) <- c("age_of_respondent",
"contraception", 
"age_of_partner", 
"wealth_index", 
"education_level",
"sex_of_household_head",
"num_of_partners", 
"religion", 
"current_contraceptive_method", 
"intention_to_use_current_contraceptive_method",
"visited_by_family_planning_worker_last_12 months", 
"visited_health_facility_last_twelve_months")
```

## Specific Data Manipulation - Creation of easy data
```{r}
#Filter out women who are older than 50 
easy_data <- new_data %>% filter(age_of_partner <= 50)

#Make a few variables binary
easy_data <- easy_data %>% mutate(age_greater_than_twenty_one = ifelse(age_of_partner > 21, 1, 0))
easy_data <- easy_data %>% mutate(contraception_yes = ifelse(contraception >= 1, 1, 0))
easy_data$age_greater_than_twenty_one <- as.factor(easy_data$age_greater_than_twenty_one)
easy_data$contraception_yes <- as.factor(easy_data$contraception_yes)
```

## Library's needed for modeling  

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(foreign)
library(tidyverse)
library(epitools)
library(lmtest)
```

## Model 0 

Blah blah blah 

```{r}
model_zero <-glm(contraception_yes ~ 1, data=easy_data, 
           family =binomial("logit"))
summary(model_zero) # Model Results + Wald Test
lrtest(model_zero)# Likelihood Ratio Test
confint(model_zero)# Confidence Interval
```

## Models with single variable 

Let $X$ be a dummy variable equal to 1 if the age of partner is greater than or equal to 21 and zero otherwise. We fit a logistic model with this covariate.
  
  $$\log\left( \frac{p}{1-p}\right) = a + bX.$$
The null hypothesis is that the contraception is the same for everyone regardless of age and can be formulated as $H_0: b =0$ vs $H_1: b \neq 0.$

```{r}
model_one <-glm(contraception_yes~age_greater_than_twenty_one, data = easy_data, 
           family =binomial("logit"))
summary(model_one) # Model Results + Wald Test
lrtest(model_one)# Likelihood Ratio Test
confint(model_one)# Confidence Interval

broom::tidy(model_one,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI
```

## Models of single variable
  
We now define $X$ to be any one variable in our data set. We regress fit the logistic models for every single variable. 

$$\log\left( \frac{p}{1-p}\right) = a + bX.$$
We want to test $H0 : b= 0$.
```{r}
#1
model_age_of_partner <-glm(contraception_yes ~ age_greater_than_twenty_one, data = easy_data, 
           family =binomial("logit"))

summary(model_age_of_partner)# Model Results + Wald Test
lrtest(model_age_of_partner)# Likelihood Ratio Test
     
#summary()# Model Results + Wald Test
#lrtest()# Likelihood Ratio Test
#confint()# Confidence Interval
#broom::tidy(,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI          
```



## Interactions

```{r}
#1
model_with_interactions <-glm(contraception_yes ~ age_greater_than_twenty_one+ as.factor(wealth_index) + as.factor(wealth_index)*age_greater_than_twenty_one, data = easy_data, 
           family =binomial("logit"))

summary(model_with_interactions)# Model Results + Wald Test
lrtest(model_with_interactions )# Likelihood Ratio Test
     
#summary()# Model Results + Wald Test
#lrtest()# Likelihood Ratio Test
#confint()# Confidence Interval
#broom::tidy(,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI 
```



### 1.2 Scatterplots with Logistic Regression Lines

After running a regression in R, it is possible to generate the predicted values of the outcome from that regression. We can plot the risks, odds, or log odds. The following lines do all three and plot the results on different graphs within the same figure. 

First, run the logistic regression model. 
```{r}
model_with_interactions <-glm(contraception_yes ~ age_greater_than_twenty_one+ as.factor(wealth_index) + as.factor(wealth_index)*age_greater_than_twenty_one, data = easy_data, 
           family =binomial("logit"))

print("Results on log OR scale")
# Results on the log OR scale
broom::tidy(model_with_interactions, 
            conf.int = TRUE)

print("Results on OR scale")
# Results on the OR scale
broom::tidy(model_with_interactions, 
            conf.int = TRUE, 
            exponentiate = TRUE)
```

#Then, generate the risk, odds, and log odds from the model.
```{r}
# Generate the model-based risk estimates
#easy_data$pred_risk <- predict(m1, # use the model to...
                          #type = "response", # predict the risk for...
                          #newdata = easy_) # the wcgs data

# Generate the model-based odds and log odds estimates
#wcgs <- wcgs %>%
  #mutate(pred_odds = pred_risk/(1-pred_risk)) %>%
  #mutate(pred_log_odds = log(pred_odds))
```

Finally, plot away!
```{r}
risk_plot <- easy_data %>%
  # the observed data from before
  ggplot(aes(x = age_greater_than_twenty_one, y = contraception_yes)) + 
  #geom_point(alpha = 0.5) + 
  # the fitted line
  geom_point() 
  # general formatting
  #scale_x_continuous("Weight (lbs)", breaks = 0:4, labels = c(unname(TeX("$\\leq 150")),
                             # "(151,160)",
                             # "(161,170)",
                              #"(171,180)",
                              #">180")) +  
  #ylab("Risk of CHD") + 
  #theme_classic()

risk_plot
```

```{r}
odds_plot <- risk_table %>%
  # the observed data from before
  ggplot(aes(x = wtcat, y = odds)) + 
  geom_point(alpha = 0.5) + 
  # the fitted line
  geom_line(aes(y = pred_odds),
            data = wcgs,
            col = "blue") + 
  # general formatting
  scale_x_continuous("Weight (lbs)", breaks = 0:4, labels = c(unname(TeX("$\\leq 150")),
                              "(151,160)",
                              "(161,170)",
                              "(171,180)",
                              ">180")) +  
  ylab("Odds of CHD") + 
  theme_classic()

log_odds_plot <- risk_table %>%
  # the observed data from before
  ggplot(aes(x = wtcat, y = log.odds)) + 
  geom_point(alpha = 0.5) + 
  # the fitted line
  geom_line(aes(y = pred_log_odds),
            data = wcgs,
            col = "blue") + 
  # general formatting
  scale_x_continuous("Weight (lbs)", breaks = 0:4, labels = c(unname(TeX("$\\leq 150")),
                              "(151,160)",
                              "(161,170)",
                              "(171,180)",
                              ">180")) +  
  ylab("Log odds of CHD") + 
  theme_classic()
```

```{r, fig.height = 6, fig.width= 8, fig.cap = "Logistic Model Results"}
grid.arrange(
  risk_plot,
  odds_plot,
  log_odds_plot,
  ncol = 2)
```


















## Model of all variables together and likelihood ratio test of nested models 
  
We now add variables $X,Y,Z, etc..$ together in the same model and regress fit the logistic model. 

$$\log\left( \frac{p}{1-p}\right) = a +bX+cY+dZ... etc$$
We want to test $H0 : b= 0$.
```{r}
model_everything <-glm(contraception_yes ~ age_of_respondent + age_of_partner + wealth_index + education_level + num_of_partners + religion + intention_to_use_current_contraceptive_method + visited_health_facility_last_twelve_months, data= easy_data, family =binomial("logit"))

summary(model_everything)# Model Results + Wald Test
lrtest(model_everything)# Likelihood Ratio Test
```


## Comparison of all the models to see which is the best

blah blah blah


```{r}

##Ahh I can't get this to work! 
lrtest(model_everything, 
model_age_of_respondent, 
model_age_of_partner, 
model_wealth_index, 
model_education_level, 
model_num_of_partners, 
model_religion, 
model_intention_to_use_current_contraceptive_method, 
model_visited_health_facility_last_twelve_months)
```