---
title: "Master RMD"
author: "James C"
date: "4/30/2020"
output: pdf_document
---


#241 Final Project

##Clean Up Data
```{r}
library(haven)
library(dplyr)
togo_data_dhs <- read_dta("togo data dhs.dta")
new_data <- togo_data_dhs
new_data <- as.data.frame(new_data)
new_data <- new_data %>% select("v012", 
"v302a", 
"mv034b_1", 
"v190", 
"mv106",
"mv151",
"mv035", 
"v130",
"v312", 
"v362", 
"v393", 
"v394", 
"v395", 
"v3a03",
"v3a04",
"v3a05")

colnames(new_data) <- c("age_of_respondent",
"contraception", 
"age_of_partner", 
"wealth_index", 
"education_level",
"sex_of_household_head",
"num_of_partners", 
"religion", 
"current_contraceptive_method", 
"intention_to_use_current_contraceptive_method",
"visited_by_family_planning_worker_last_12 months", 
"visited_health_facility_last_12 months",
"at_health_facility_told_of_family_planning", 
"told_about_side_effects_by_health_or_family_planning_worker", 
"told_how_to_deal_with_side_effects", 
"told_about_other_family_planning_methods")
```

## Specific Data Manipulation - Creation of easy data
```{r}
#Filter out women who are older than 50 
easy_data <- new_data %>% filter(age_of_respondent <= 50)
easy_data <- easy_data %>% mutate(age_greater_than_twenty_one = ifelse(age_of_respondent > 21, 1, 0))
easy_data <- easy_data %>% mutate(contraception_yes = ifelse(contraception >= 1, 1, 0))
easy_data$age_greater_than_twenty_one <- as.factor(easy_data$age_greater_than_twenty_one)
easy_data$contraception_yes <- as.factor(easy_data$contraception_yes)
```




## Library's needed for modeling  

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(foreign)
library(tidyverse)
library(epitools)
library(lmtest)
```

## Model 0 

Blah blah blah 

```{r}
model_zero <-glm(contraception_yes ~ 1, data=easy_data, 
           family =binomial("logit"))
summary(model_zero) # Model Results + Wald Test
lrtest(model_zero)# Likelihood Ratio Test
confint(model_zero)# Confidence Interval
```

## First Model

Let $X$ be a dummy variable equal to 1 if the age of partner is greater than or equal to 21 and zero otherwise. We fit a logistic model with this covariate.
  
  $$\log\left( \frac{p}{1-p}\right) = a + bX.$$
The null hypothesis is that the contraception is the same for everyone regardless of age and can be formulated as $H_0: b =0$ vs $H_1: b \neq 0.$

```{r}
model_one <-glm(contraception_yes~age_greater_than_twenty_one, data = easy_data, 
           family =binomial("logit"))
summary(model_one) # Model Results + Wald Test
lrtest(model_one)# Likelihood Ratio Test
confint(model_one)# Confidence Interval

broom::tidy(model_one,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI
```

## Second Model
  
We now define $X$ to be a variable taking the age of the individual in togo and let us regress fit the logistic model

$$\log\left( \frac{p}{1-p}\right) = a + bX.$$
We want to test $H0 : b= 0$.
```{r}
model_two <-glm(contraception_yes ~ age_of_respondent, data = easy_data, 
           family =binomial("logit"))

summary(model_two)# Model Results + Wald Test
lrtest(model_two)# Likelihood Ratio Test
confint(model_two)# Confidence Interval


broom::tidy(model_two,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI
```


## Third Model
  
We now define a variable $Y$ to be a variable describing the wealth of an individual in togo and let us regress fit the logistic model. 

$$\log\left( \frac{p}{1-p}\right) = a + cY.$$
We want to test $H0 : b= 0$.
```{r}
model_three <-glm(contraception_yes ~ wealth_index, data = easy_data, 
           family =binomial("logit"))

summary(model_three)# Model Results + Wald Test
lrtest(model_three)# Likelihood Ratio Test
confint(model_three)# Confidence Interval


broom::tidy(model_three,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI
```


## Fourth Model
  
We now define a variable $Z$ to be a variable describing the number of partners of an individual in togo and let us regress fit the logistic model. 

$$\log\left( \frac{p}{1-p}\right) = a +dZ.$$
We want to test $H0 : b= 0$.
```{r}
model_four <-glm(contraception_yes ~ num_of_partners, data = easy_data, 
           family =binomial("logit"))

summary(model_four)# Model Results + Wald Test
lrtest(model_four)# Likelihood Ratio Test
confint(model_four)# Confidence Interval


broom::tidy(model_four,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI
```

## Fifth Model
  
We now add variables $X,Y,Z$ together in the same model and regress fit the logistic model. 

$$\log\left( \frac{p}{1-p}\right) = a +bX+cY+dZ.$$
We want to test $H0 : b= 0$.
```{r}
model_five <-glm(contraception_yes ~ age_of_respondent + wealth_index+num_of_partners, data = easy_data, 
           family =binomial("logit"))

summary(model_five )# Model Results + Wald Test
lrtest(model_five )# Likelihood Ratio Test
confint(model_five )# Confidence Interval


broom::tidy(model_five,conf.int = TRUE,exponentiate = TRUE) #Odds ratio and it's 95% CI
```


## Comparison of all the models to see which is the best

blah blah blah
```{r}
lrtest(model_zero, model_one, model_two, model_three, model_four, model_five)
```